%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart
    %\resumeProjectHeading
    %{\textbf{RENCAT (Remote, Noninvasive, Cardiac Activity Tracer)} $|$ \emph{Python, Raspberry Pi, Linux}} {}
    %\resumeItemListStart
        %\resumeItem {A NASA Prototype which utilizes a novel laser vibrometer sensor for monitoring cardiac activities remotely and non-%invasively, specifically heart functions of valve/chamber opening and closing cycles (cardiac cycles)}
        %\resumeItem {Designed software that analyzes and filters the readings from an interferometer and developed a program that uses cardiac data to mimic a heartbeat onto a speaker}
        %\resumeItem{U.S. Patent Number: 11,119,072 $|$ Tops Document: LAR-TOPS-315}
    %\resumeItemListEnd
    \resumeProjectHeading
    {\textbf{AttendEase} $|$ \emph{React, Firebase, TailwindCSS, Swift.js}}{}
    \resumeItemListStart
        \resumeItem{Piloted the development of an attendance management system that utilizes NFC technology to check students into the course. Designed an attendance dashboard that shows instructors' students' attendance statistics, creating high-end reports notifying the instructor of absences and tardies.}
        \resumeItem{iOS and Android apps were also developed to emit an NFC signal from the phone which they can scan to let students check into their lectures for ease of usability.} 
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Gamified Silk Screen Cleaner} $|$ \emph{Python, Raspberry Pi, Linux}}{}
    \resumeItemListStart
        \resumeItem{Placed 1st at the NYSID (New York State Industries for the Disabled) competition by providing a high-tech solution for cleaning plastisol ink from screen printing equipment, designed to assist workers with disabilities. The solution improved workplace efficiency by 40\%.}
        \resumeItem{Video: \href{https://www.youtube.com/watch?v=x-vOqySdoQI}{\underline{https://www.youtube.com/watch?v=x-vOqySdoQI}} } 
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{Dragonfly Drone Software} $|$ \emph{Python, Tensorflow, SQL, Pyodbc}}{}
    \resumeItemListStart
        \resumeItem{Developed and optimized the Dragonfly drone software system using Python, integrating AI-powered image recognition and geolocation algorithms to enable autonomous navigation and precise delivery.}
        \resumeItem{Engineered a comprehensive image database and recall mechanism, allowing the drone to accurately identify, store, and revisit specific locations. The use of artificial intelligence enhances the drone's ability to deliver packages, such as medicine or seeds, with high accuracy and reliability.} 
    \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{XpressAssist} $|$ \emph{ASP.NET, C\#, HTML, CSS, JavaScript, MSSQL}}{}
    \resumeItemListStart
        \resumeItem{Developed a web-based software solution that features a web-based clocking-in system for employees to view their workstation daily, with mobile notifications for managers and support workers.}
        \resumeItem{Employees can also request assistance or notify about breaks, while managers receive weekly reports and use a data prediction model to gauge task engagement and potential communication challenges.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
